Local PCA Shows How Population Structure Differs Along the Genome

### 2016-06-22 writeup/local_pca_paper.tex
update

\begin{figure}
    \begin{center}
       \includegraphics[width=0.8\textwidth]{FigS_pca_plots_for_Medicago_allchr_3peaks_byMDS}
    \end{center}
    \caption{
        PCA plots for all 8 chromosomes' 3 peaks in \textit{Medicago truncatula}.
        \label{fig:pca_peaks_medicago_allchr}
    }
\end{figure}

>>>>

\begin{figure}
    \begin{center}
       \includegraphics[width=0.82\textwidth]{FigS_pca_plots_for_Medicago_allchr_3peaks_byMDS}
    \end{center}
    \caption{
        PCA plots for all 8 chromosomes' 3 peaks in \textit{Medicago truncatula}.
        \label{fig:pca_peaks_medicago_allchr}
    }
\end{figure}

\begin{figure}
    \begin{center}
       \includegraphics[width=1\textwidth]{FigS_pca_plots_allchr_drosophila}
    \end{center}
    \caption{
        PCA plots for chromosome arms 2L, 2R, 3L, 3R and X in \textit{Drosophila}.
        \label{fig:pca_drosophila_allchr}
    }
\end{figure}

\begin{figure}
    \begin{center}
       \includegraphics[width=0.9\textwidth]{FigS_pca_plot_allchr_human}
    \end{center}
    \caption{
        PCA plots for all 22 autosomes in human.
        \label{fig:pca_human_allchr}
    }
\end{figure}

\begin{figure}
    \begin{center}
       \includegraphics[width=1\textwidth]{FigS_pca_plots_medicago_allchr}
    \end{center}
    \caption{
        PCA plots for all 8 chromosomes in \textit{Medicago truncatula}.
        \label{fig:pca_medicago_allchr}
    }
\end{figure}
